---
output:
  pdf_document: default
  html_document: default
---

# Load data
```{r}
fifa <- read.csv('data.csv')
#head(fifa,10)
```

The goal of the project is to predict the Wage of a player based on stats

# Select variables in data having player stats
```{r}
colnames <- c("Wage","Potential","Crossing","Finishing","HeadingAccuracy","Dribbling","Stamina","Strength","LongShots","Aggression","Positioning","Penalties","SlidingTackle")
fifa_subset <- fifa[,colnames]
```


# Exploratory Data Analysis

# Checking for missing values in the data frame
```{r}
sapply(fifa_subset, function(x) sum(is.na(x)))
```
There are missing data.

# Omit NA values
```{r}
fifa_subset_complete <- na.omit(fifa_subset)
```


# Checking if missing values in the data frame have been omited
```{r}
sapply(fifa_subset_complete, function(x) sum(is.na(x)))
```

# Checking the data type of each variable in the data set
```{r}
sapply(fifa_subset_complete, function(x) typeof(x))
```


# Summary statistics of each column in the data frame.
```{r}
#summary(fifa_subset)
```

# Convert wage into integer in thousands of euros
```{r}
fifa_subset_complete[,"Wage"] <- as.integer(gsub("[^0-9]", "", fifa_subset_complete$Wage) )
```


# Summary statistics of each column in the data frame.
```{r}
summary_stata <- lapply( fifa_subset_complete , function(x) rbind( mean = mean(x) ,
                                                                   sd = sd(x) ,
                                                                   median = median(x) ,
                                                                   minimum = min(x) ,
                                                                   maximum = max(x) ,
                                                                   s.size = length(x) ) )

summary_stata_df <- data.frame(summary_stata)
summary_stata_df
```


# Explore association between variables in the data frame using correlation matrix

```{r}
cor_matrix <- as.data.frame(cor(fifa_subset_complete))
cor_matrix
```


# Check if the response variable is close to normality
```{r}
plot(density(fifa_subset_complete$Wage), main = "Density plot of wage", ylab = "Frequency",
    col="red", xlab = "wages of player in thousands of euros")
```

# Explore the association between the dependent variable and the independent variable 
# using scatterplot matrix
```{r}
pairs(fifa_subset_complete[,c("Wage","Potential","Crossing","Finishing")], main = "Scatterplot Matrix")
```



```{r}
pairs(fifa_subset_complete[,c("Wage","HeadingAccuracy","Dribbling","Stamina")], main = "Scatterplot Matrix")
```



```{r}
pairs(fifa_subset_complete[,c("Wage","Strength","LongShots","Aggression")], main = "Scatterplot Matrix")
```



```{r}
pairs(fifa_subset_complete[,c("Wage","Positioning","Penalties","SlidingTackle")], main = "Scatterplot Matrix")
```

# Splitting the data frame into the Training set and Testing set
# install.packages('caTools')
```{r}
library(caTools)
set.seed(2019)
split = sample.split(fifa_subset_complete$Wage, SplitRatio = 0.7)
training_set = subset(fifa_subset_complete, split == TRUE)
testing_set = subset(fifa_subset_complete, split == FALSE)
```


# Fitting Multiple Linear Regression to the Training set
```{r}
linear_model = lm(formula = Wage ~ ., data = training_set)
linear_model
```


# Coefficients Estimates for the Linear Regression Model
```{r}
linreg_coef <- as.data.frame(summary(linear_model)$coef)
linreg_coef
```


# Statistical Summary of the model
```{r}
summary(linear_model)
```


# Predicting new result with linear multiple Regression
```{r}
y_pred = predict(linear_model, newdata = testing_set[,-1])
```

# Calculate prediction accuracy of the multiple linear regression
```{r}
cor(testing_set$Wage, y_pred) # 51.87%
```


# Fitting Decision Tree Regression to the dataset
```{r}
# install.packages('rpart')
# install.packages("rpart.plot")
library(rpart)
library(rpart.plot)
decision_tree_regression = rpart(formula = Wage ~ ., data = training_set)
rpart.plot(decision_tree_regression)
```


# Predicting new result with Decision Tree Regression
```{r}
y_pred_DT = predict(decision_tree_regression, newdata = testing_set[,-1])
```


# Calculate prediction accuracy of the decision tree
```{r}
cor(testing_set$Wage, y_pred_DT) # 68.79%
```



# Fitting Random Forest Regression to the dataset
```{r}
# install.packages('randomForest')
library(randomForest)
set.seed(2019)
random_forest_regression = randomForest(x = training_set[-1],
                                        y = training_set$Wage,
                                        ntree = 500)
```



# Predicting a new result with Random Forest Regression
```{r}
y_pred_RF = predict(random_forest_regression, newdata = testing_set[,-1])
```


# Calculate prediction accuracy of the random forest
```{r}
cor(testing_set$Wage, y_pred_RF) # 82.47%
```

